---
title: "Alcohol vs Seat choice"
author: "Steven Garcia"
date: "Fall 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row you choose to sit in??

# Introduction

$H_0$ There is no difference between the alcohol consumed based on the row you sit in.

$H_A$ There is a difference between the alcohol consumed based on the row you sit in.

# Methods

The response variable is numerical based on the amount of alcohol consumed and the explanitory variable is categorical. Therefore we use the numerical~cat. 

## Results

### Graphical Results


### Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
The box plot indicates the average amount of alcohol consumed was around 1-5 drinks. Compared to the back row that had a mean of alcohol consumed was 15. TThe front and middle seat have little difference between the amount of alcohol consumed. 
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

The graph shows that the people in the back consume 3 times more alcohol compared to the front and middle rows/seats. 

## Numerical Summarys 

## Inferential Tests

## Conclusions


